\section{Introduction}
\label{sec:intro}

Crowdsensing has become more and more popular, one reason is that mobile devices are becoming increasingly powerful with media processing capable. In fact, a phone has been a small media center, storing all kinds of media files, like videos, images and so on. Consider a scenario that we need to get some photos or video clips of specified information from the mobile phone directly and realtime, because we can't store all the media in the cloud and not necessary to do so, the intuition for this is to search contents on phone over wireless connection. So we want to build a query server that process queries and get the requested photos from the phones. Instead storing all the media files on the server, we can store the meta data of the media files on it. Here, we need the phones to process the media files and get their meta data first and upload to the query server.

Our work focuses on the design of this query service architecture. Let's discuss the query first, sometimes, one may need to have more knowledge of what happened in certain time and place. So time interval and location should be an essential aspect in queries. And in some scenarios, like army, they want to know whether there exist events in specified time and location, such as any person entered building, any car drove through and so on. To thoroughly describe an event there, we include the demands in the query, so we define query as a vector, $\overrightarrow{\mathbf{Q}}$=(time, location, objects, action(objects combination), deadline). After the query server received the queries, then it begins to process the meta-data based on queries. How to find the best fit photos? Since mobile phones' uploading speed is limited and query's deadline is firm, there exists a case that even some photos are qualified, we can't upload all to the server. Here comes another difficulty, how to select from these photos. Our goal is to get as much information for the query, one intuition is to make qualified photos as diverse as possible. For this, we define "similarity" among photos, so we aim to select a subset of photos that satisfy least similarity requirement. 